VOCC outline

### 2020-04-24 ms/ms.Rmd
Add comment and example to caption

(ref:chop-panel) Maps of biotic (top), temperature (middle), and DO (bottom) trends underlying interaction plots (between map rows) of predicted biotic trend (y-xis) for each standard deviation change in seafloor temperature and DO (x-axis) for mature populations of species representing a range of taxonomic groups and response patterns. Colours and lines in the interaction plots match the slopes represented in Fig. \@ref(fig:worm-plots), where low (0.025) and high (0.975) quantiles of mean climate conditions are illustrated in blue and red for temperatures and yellow and purple for DO.
For example, for Widow Rockfish, TODO: walk through the temperature panels.

>>>>

(ref:chop-panel) Maps of biotic (top), temperature (middle), and DO (bottom) trends underlying interaction plots (between map rows) of predicted biotic trend (y-xis) for each standard deviation change in seafloor temperature and DO (x-axis) for mature populations of species representing a range of taxonomic groups and response patterns. Colours and lines in the interaction plots match the slopes represented in Fig. \@ref(fig:worm-plots), where low (0.025) and high (0.975) quantiles of mean climate conditions are illustrated in blue and red for temperatures and yellow and purple for DO.
Black lines are shown when TODO.
As an example, for Widow Rockfish, we estimate that biomass density has increased with increasing temperatures in cooler regions and decreased with increasing temperatures in warmer regions.

<!-- SA: I almost wonder if we should show these chopstick plots before the moderately overwhelming slopes for all the species. Not sure, I can see an argument either way. Maybe at least allude in the caption for the coefficient plot that this next plot exists and may help with interpretation.

The alternative would be to help the reader along by giving some examples like in this chopstick plot, and then zooming out to show the coefficients for all the species.
-->
